Refining character relationships using embeddings of textual units : a case study on Les Misérables

### 2022-10-01 article/paper1.tex
write article

>>>>

The next results can be found in Table 5 and Table 6. In fact, they are just the transposed results from previous table, with the top 5 characters based objects displayed for a set of words. This type of results can be seen as "queries" an user could make in order to find the most associated objects. We chose here to show the most associated objects to the words "aimer", "rue", "justice" and "guerre", as they represent some of the major topic of the book. Surprisingly, in this task, the \textbf{CA-CENT} method give quite poor results compared to the \textbf{CA-REG}. In the latter, the main love relationship (Cosette-Marius) of the book is the most associated object for "aimer", several "amis de l'ABC" (a revolutionary group) are most associated with "rue", the cop-suspect relationship (Javert-Valjean) is the top object for "justice", and officers or aggressive characters appear massively associated with "guerre". Thus this seems like convincing results.
